---
title: "Automorphism_Groups"
author: "Jeff Lansing"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Automorphism_Groups}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
require(magrittr)
require(stringr)
require(knitr)
require(kableExtra)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
.caption {
  margin: auto;
  text-align: center;
}
```
```{r setup, echo = FALSE, warning=FALSE}
library(stringr)
library(magrittr)
library(spantreeorbits)
source("./rgl_setup.R")
rgl::setupKnitr(autoprint = TRUE)
```

```{=html}
<script type="text/javascript" id="MathJax-script" async
  src="https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js">
</script>
```

## Introduction

The goal of this vignette is to generate automorphism groups that correspond to the alignments described in the [Pair_Alignment](Pair_Alignment.html) vignette.

## Alignment of the Tetrahedron and the Dual Tetrahedron

```{r get_polys, echo=FALSE}
data(tetrahedron, package = "spantreeorbits")
data(cube, package = "spantreeorbits")
data(octahedron, package = "spantreeorbits")
data(dual_tetrahedron, package = "spantreeorbits")
data(rhombic_dodecahedron, package = "spantreeorbits")
data(deltoidal_icositetrahedron, package = "spantreeorbits")
data(rhombicuboctahedron, package = "spantreeorbits")
data(deltoidal_tetracontaoctahedron, package = "spantreeorbits")
```

The tetrahedron and the dual tetrahedron are aligned by the neighbor map from the rhombic dodecahedron, which maps the vertices of the tetrahedron to the vertices of the dual tetrahedron based on the connection of their edges,  which is identifed by the octahedron.

```{r}
rad_map <- rhombic_dodecahedron$nghmap
```
```{r echo=FALSE}
rad_map %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:4), width = "1.5em")
```

This table has 3 aspects: (i) there are the left 2 columns with the ids of the vertices of the tetrahedron, (ii) there are the right 2 columns with the ids of the vertices of the dual tetrahedron, and (iii) there are the 6 rows, which show the alignment.

Each of these 3 aspects of the neighbor map has an associated automorphism group.


```{r}
am_left <- rhombic_dodecahedron$nghmap[,1:2] %>% edgelist_to_adjmat()
```
```{r echo=FALSE}
am_left %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:4), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
lf_gr <- am_left %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- lf_gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The left polyhedron has ", nst, " spanning trees")
```

The left 2 columns of the map are represented as an adjacency matrix, which can then be used (by the GAP GRAPE package) to create an automorphism graph.

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell2">
<script type="text/x-sage">
A := [[0,1,1,1],[1,0,1,1],[1,1,0,1],[1,1,1,0]];;
gamma := Graph( Group(()), [1..4], OnPoints, function(x,y) return A[x][y]=1;; end, true );;
lag := AutGroupGraph( gamma );
Display(StructureDescription(lag));
sg :=StrongGeneratorsStabChain(StabChain(lag));
oh := Group(sg);;
Display(oh);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell2',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell2').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```
In this GAP code, we create the automorpnism group, then we arrange the elements of the group by conjugacy class, and then we identify which elements are strong generators of the group.

Next we look at the right half of the neighbor map.

```{r}
am_rt <- rhombic_dodecahedron$nghmap[,3:4] %>% edgelist_to_adjmat()
```
```{r echo=FALSE}
am_rt %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:4), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
rt_gr <- am_rt %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- rt_gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The right polyhedron has ", nst, " spanning trees")
```

Here we see that the right 2 columns of the map have the same adjacency matrix representation as the left 2 columns, so this technique cannot be used to get a distinct automorphism group for the dual tetrahedron. We will return to this issue below.

First we create an automorphism group for the octahedron, using the technique as before.

```{r}
am_oct <- octahedron$faces %>% apply(1, function(rw) {
      rw[c(1,2,2,3,3,1)] #get the edges around each face
    }) %>% as.integer() %>% matrix(byrow = T, ncol = 2) %>% #combine them in a matrix
    get_set() %>% as.list() %>% unlist() %>% # remove duplicates
  matrix(byrow = T, ncol = 2) %>% edgelist_to_adjmat() # and convert to an adjacency matrix

```
```{r echo=FALSE}
am_oct %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:6), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
oct_gr <- am_oct %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- oct_gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The octahedron has ", nst, " spanning trees")
```

We convert the octahedron adjacency matrix to a GAP list of lists, and call it *"A"*. This can be plugged into a call to GAP.

```{r}
am <- am_oct %>% apply(1, function(rw) { 
    str_c(rw, collapse = ',') %>% str_c('[', ., ']')
  }) %>% str_c(collapse = ',') %>% str_c('A := [', ., '];;gamma := Graph( Group(()), [1..6], OnPoints, function(x,y) return A[x][y]=1;; end, true );;ag := AutGroupGraph( gamma );')
am

```

In this case the adjacency matrix is a $6 \times 6$ matrix. We use it to generate a group.

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell4">
<script type="text/x-sage">
A := [[0,1,1,1,1,0],[1,0,1,0,1,1],[1,1,0,1,0,1],[1,0,1,0,1,1],[1,1,0,1,0,1],[0,1,1,1,1,0]];;
gamma := Graph( Group(()), [1..6], OnPoints, function(x,y) return A[x][y]=1;; end, true );;
ag := AutGroupGraph( gamma );
Display(StructureDescription(ag));
sg :=StrongGeneratorsStabChain(StabChain(ag));
oh := Group(sg);;
Display(oh);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell4',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell4').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

Returning to automorphism group for the dual tetrahedron, we can proceed as follows:

* using the automorphism group of the octahedron just generated
  + Copy the group definition
  + compute the normal subgroups of that group
  + identify which 2 normal subgroups we want to use (we already know they will be isomorphic to $S_4$)
  + make sure they are really different groups
  
```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell3">
<script type="text/x-sage">
pr:=Group( [ (3,5), (2,3)(4,5), (1,2)(4,6) ] );;
nsg:=NormalSubgroups(pr);;
Display(List(nsg,StructureDescription));
u34:=Group(Union(Elements(nsg[3]), Elements(nsg[4])));;
i34:=Group(Intersection(Elements(nsg[3]), Elements(nsg[4])));;
Print(StructureDescription(u34), ", ", StructureDescription(i34));
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell3',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell3').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

We identify 2 copies of $S_4$ as the third and fourth items in the list of normal subgroups. Here it is evident that the two copies of $S_4$ are different, because their union behaves differently from their intersection. (If the 2 copies were the same, their union and their intersection would also be the same.)

The following element table shows another view of the same idea.

```{r results ='asis', echo=FALSE}
path <- system.file("extdata", "c2s4oct.txt", package = "spantreeorbits", mustWork = TRUE)
gaptext <- readLines(con = path) 
cn <-  eval(parse(text = str_c(gaptext[4],collapse = '') %>% 
                    str_replace_all("# \\[", "c(") %>% 
                    str_replace_all("\\]", ")")))
ci <-  eval(parse(text = gaptext[5] %>% str_replace_all("# \\[", "c(") %>% 
                    str_replace_all("\\]", ")")))
names <- c()
for(j in 1:length(ci)) {
  names <- c(names, str_c(cn[j],'.',1:ci[j]))
}

lf <- c(1,11,12,15,16,13,14,17,18,19,20,21,24,25,22,23,26,29,31,32,30,33,27,28)
rt <- c(1,5,6,7,8,9,10,17,18,19,26,28,31,33,30,29,32,27,42,43,44,45,46,47)
is <- c(1,17,18,19,26,27,31,30,28,29,32,33)
ot <- c(1,2,3,4,17,18,19,26,27,31,30,34,35,39,38,28,29,32,33,37,36,41,40,48)

colors <- rep("LightGrey", 48)
colors[ot] <- "LightGreen"
colors[lf] <- "LightBlue"
colors[rt] <- "Khaki"
colors[is] <- "LightCoral"

t <- gaptext[9:(length(gaptext)-1)] %>% 
    str_replace_all('-1', '{-1}') %>% 
    str_replace_all('x1', 'a') %>% 
    str_replace_all('x2', 'b') %>%
    str_replace_all('x3', 'c') %>%
    str_replace_all('\\*', '') %>%
    str_replace('\\<', '') %>%
    str_replace(' ...>', '') %>% 
    # str_c('"$$\\\\colorbox{yellow}{$', ., '$}$$"') %>%
    str_c('"', ., '"') %>%
    str_c(collapse=',') %>% str_c('c(', ., ')')
vals <- eval(parse(text = t))

for(i in 1:48) {
  vals[i] <-  str_c(names[i], "&nbsp;$$\\require{color}\\colorbox{", colors[i], "}{$", vals[i], "$}$$")
}

knitr::kable(
  matrix(vals,6,8),
  caption = "C2xS4 with normal subgroups: green C2xA4, red A4, blue S4 left, beige S4 right. Identifiers are based on conjugacy classes.",
  format = "html",
  escape = FALSE,
  align = 'c',
  col.names = NULL
)

```

This element table used the following GAP code.

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell3b">
<script type="text/x-sage">
ElsByConjClass:=function(G)
  local els,cc,c,x;
  cc := ConjugacyClasses(G);
  els := [];
  for c in cc do
    for x in c do
      Add(els, x);
    od;
  od;
  return rec(names := ClassNames(CharacterTable(G)), sizes := List(cc, Size), elements := els);
end;;

GetElIx:=function(NS, i, j, k) 
  local emb, ecci, eccj;
  ecci := ElsByConjClass(NS[i]).elements;
  emb := IsomorphicSubgroups(NS[i], NS[j]);
if Length(emb) < k then return []; fi;
  eccj := ElsByConjClass(Image(emb[k])).elements;
  return List(eccj, x -> Position(ecci, x));
end;;

pr:=Group( [ (3,5), (2,3)(4,5), (1,2)(4,6) ] );;
nsg:=NormalSubgroups(pr);;

lp2 := GetElIx(nsg,1,2,1);;
lp3 := GetElIx(nsg,1,3,1);;
lp4 := GetElIx(nsg,1,4,2);;
lp6 := GetElIx(nsg,1,6,1);;
Print(lp2, "\n", lp3, "\n", lp4, "\,", lp6);

els := ElsByConjClass(pr);;
Print(StructureDescription(pr), "\n");
Print(els.names, "\n# ", els.sizes, "\n");
for e in els.elements do
Print(Factorization(pr, e),"\n");
od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell3b',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell3b').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

We can start to analyze the element table by looking at the distribution of the conjugacy classes among the normal subgroups.

```{r echo=FALSE}

get_ix <- function(ids) {
  nm <- names[ids] %>% str_extract_all("^..") %>% unlist() %>% unique()
  which(cn %in% nm)
}

ids <- list(ot, lf, rt, is)
mx <- matrix(0,5,10) %>% `colnames<-`(cn) %>% 
  `rownames<-`(c("C2xA4", "S4_lf", "S4_rt", "A4", "gens"))
for(i in 1:4){for(j in get_ix(ids[[i]])){mx[i,j] <- ci[j]}}
mx[5,2] <- 1 # generator a
mx[5,3] <- 2 # generators b and c

knitr::kable(
  mx,
  caption = "Distribution of conjugacy classes and generators in normal subgroups of C2xS4",
  format = "html",
  align = "c"
) %>% kableExtra::kable_styling(
  bootstrap_options = c("striped","bordered"), 
  full_width = F, position = "left") %>% 
  kableExtra::column_spec(c(1:10), width = "3em")
```
The fact that the generators are not in both $S_4$ subgroups is interesting, as will be seen in another vignette.


## Alignment of the Cube and the Octahedron

As above, each of the 3 aspects of the neighbor map has an associated automorphism group.


```{r}
am_dit_lf <- deltoidal_icositetrahedron$nghmap[,1:2] %>% edgelist_to_adjmat()
```

```{r echo=FALSE}
am_dit_lf %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:8), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
gr <- am_dit_lf %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The left polyhedron has ", nst, " spanning trees")
```

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell5">
<script type="text/x-sage">
A := [[0,1,0,1,0,1,0,0],[1,0,1,0,0,0,1,0],[0,1,0,1,0,0,0,1],[1,0,1,0,1,0,0,0],[0,0,0,1,0,1,0,1],[1,0,0,0,1,0,1,0],[0,1,0,0,0,1,0,1],[0,0,1,0,1,0,1,0]];;
gamma := Graph( Group(()), [1..8], OnPoints, function(x,y) return A[x][y]=1;; end, true );;
lag := AutGroupGraph( gamma );
Display(StructureDescription(lag));
sg :=StrongGeneratorsStabChain(StabChain(lag));
oh := Group(sg);;
Display(oh);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell5',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell5').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

```{r}
am_dit_rt <- deltoidal_icositetrahedron$nghmap[,3:4] %>% edgelist_to_adjmat()
```

```{r echo=FALSE}
am_dit_rt %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:6), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
gr <- am_dit_rt %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The right polyhedron has ", nst, " spanning trees")
```

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell6">
<script type="text/x-sage">
A := [[0,1,1,1,1,0],[1,0,1,0,1,1],[1,1,0,1,0,1],[1,0,1,0,1,1],[1,1,0,1,0,1],[0,1,1,1,1,0]];;
gamma := Graph( Group(()), [1..6], OnPoints, function(x,y) return A[x][y]=1;; end, true );;
rag := AutGroupGraph( gamma );
Display(StructureDescription(rag));
sg :=StrongGeneratorsStabChain(StabChain(rag));
oh := Group(sg);;
Display(oh);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell6',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell6').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

```{r}
am_co <- c(
    cuboctahedron$cu_faces %>% apply(1, function(rw) {
      rw[c(1,2,2,3,3,4,4,1)]
    }) %>% as.integer(),
    cuboctahedron$oct_faces %>% apply(1, function(rw) {
      rw[c(1,2,2,3,3,1)]
    }) %>% as.integer()
  ) %>% matrix(byrow = T, ncol = 2) %>% get_set() %>% 
    as.list() %>% unlist() %>% 
matrix(byrow = T, ncol = 2) %>% edgelist_to_adjmat()

```

```{r echo=FALSE}
am_co %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:12), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
gr <- am_co %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The cuboctahedron has ", nst, " spanning trees")
```

We convert the cuboctahedron adjacency matrix to a GAP list of lists, and call it *"A"*. This can be plugged into a call to GAP.

```{r}
am <- am_co %>% apply(1, function(rw) { 
    str_c(rw, collapse = ',') %>% str_c('[', ., ']')
  }) %>% str_c(collapse = ',') %>% str_c('A := [', ., '];;gamma := Graph( Group(()), [1..12], OnPoints, function(x,y) return A[x][y]=1;; end, true );;ag := AutGroupGraph( gamma );')
am

```

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell7">
<script type="text/x-sage">
A := [[0,1,1,0,0,0,0,0,1,0,1,0],[1,0,0,1,1,0,0,0,0,0,1,0],[1,0,0,1,0,0,1,0,1,0,0,0],[0,1,1,0,1,0,1,0,0,0,0,0],[0,1,0,1,0,1,0,0,0,0,0,1],[0,0,0,0,1,0,1,1,0,0,0,1],[0,0,1,1,0,1,0,1,0,0,0,0],[0,0,0,0,0,1,1,0,1,1,0,0],[1,0,1,0,0,0,0,1,0,1,0,0],[0,0,0,0,0,0,0,1,1,0,1,1],[1,1,0,0,0,0,0,0,0,1,0,1],[0,0,0,0,1,1,0,0,0,1,1,0]];;
gamma := Graph( Group(()), [1..12], OnPoints, function(x,y) return A[x][y]=1;; end, true );;
ag := AutGroupGraph( gamma );
Display(StructureDescription(ag));
sg :=StrongGeneratorsStabChain(StabChain(ag));
oh := Group(sg);;
Display(oh);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell7',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell7').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

## Alignment of the Rhonbic Dodecahedron and the Cuboctahedron

Again, each of the 3 aspects of the neighbor map has an associated automorphism group.


```{r}
am_dtc_lf <- deltoidal_tetracontaoctahedron$nghmap[,1:2] %>% edgelist_to_adjmat()
```

```{r echo=FALSE}
am_dtc_lf %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:14), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
gr <- am_dtc_lf %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The left polyhedron has ", nst, " spanning trees")
```

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell8">
<script type="text/x-sage">
A := [[0,0,0,0,0,0,1,0,0,1,0,1,1,0],[0,0,0,0,0,0,1,1,0,0,1,0,1,0],[0,0,0,0,0,0,1,0,1,0,1,1,0,0],[0,0,0,0,0,0,0,0,1,1,0,1,0,1],[0,0,0,0,0,0,0,1,0,1,0,0,1,1],[0,0,0,0,0,0,0,1,1,0,1,0,0,1],[1,1,1,0,0,0,0,0,0,0,0,0,0,0],[0,1,0,0,1,1,0,0,0,0,0,0,0,0],[0,0,1,1,0,1,0,0,0,0,0,0,0,0],[1,0,0,1,1,0,0,0,0,0,0,0,0,0],[0,1,1,0,0,1,0,0,0,0,0,0,0,0],[1,0,1,1,0,0,0,0,0,0,0,0,0,0],[1,1,0,0,1,0,0,0,0,0,0,0,0,0],[0,0,0,1,1,1,0,0,0,0,0,0,0,0]];;
gamma := Graph( Group(()), [1..14], OnPoints, function(x,y) return A[x][y]=1;; end, true );;
lag := AutGroupGraph( gamma );
Display(StructureDescription(lag));
sg :=StrongGeneratorsStabChain(StabChain(lag));
oh := Group(sg);;
Display(oh);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell8',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell8').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

```{r}
am_dtc_rt <- deltoidal_tetracontaoctahedron$nghmap[,3:4] %>% edgelist_to_adjmat()
```

```{r echo=FALSE}
am_dtc_rt %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:12), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
gr <- am_dtc_rt %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The right polyhedron has ", nst, " spanning trees")
```

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell9">
<script type="text/x-sage">
A := [[0,1,1,0,0,0,0,0,1,0,1,0],[1,0,0,1,1,0,0,0,0,0,1,0],[1,0,0,1,0,0,1,0,1,0,0,0],[0,1,1,0,1,0,1,0,0,0,0,0],[0,1,0,1,0,1,0,0,0,0,0,1],[0,0,0,0,1,0,1,1,0,0,0,1],[0,0,1,1,0,1,0,1,0,0,0,0],[0,0,0,0,0,1,1,0,1,1,0,0],[1,0,1,0,0,0,0,1,0,1,0,0],[0,0,0,0,0,0,0,1,1,0,1,1],[1,1,0,0,0,0,0,0,0,1,0,1],[0,0,0,0,1,1,0,0,0,1,1,0]];;
gamma := Graph( Group(()), [1..12], OnPoints, function(x,y) return A[x][y]=1;; end, true );;
rag := AutGroupGraph( gamma );
Display(StructureDescription(rag));
sg :=StrongGeneratorsStabChain(StabChain(rag));
oh := Group(sg);;
Display(oh);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell9',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell9').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

```{r}
am_rco <- rhombicuboctahedron$edges %>% edgelist_to_adjmat()

```

```{r echo=FALSE}
am_rco %>% kableExtra::kbl() %>% kableExtra::column_spec(c(2:24), width = "1.5em")
```

```{r echo=FALSE, class.output="bg-info"}
rco_gr <- am_rco %>% igraph::graph_from_adjacency_matrix(mode = 'undirected')
lap <- rco_gr %>% igraph::laplacian_matrix(sparse = F)
nst <- lap[2:nrow(lap),2:ncol(lap)] %>% `dimnames<-`(list(NULL, NULL)) %>% det()
str_c("The rhombicuboctahedron has ", bit64::as.integer64(nst) + 1, " spanning trees")
```

We convert the rhombicuboctahedron adjacency matrix to a GAP list of lists, and call it *"A"*. This can be plugged into a call to GAP.

```{r}
am <- am_rco %>% apply(1, function(rw) { 
    str_c(rw, collapse = ',') %>% str_c('[', ., ']')
  }) %>% str_c(collapse = ',') %>% str_c('A := [', ., '];;gamma := Graph( Group(()), [1..24], OnPoints, function(x,y) return A[x][y]=1;; end, true );;ag := AutGroupGraph( gamma );')
am

```

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell10">
<script type="text/x-sage">
A := [[0,1,1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0],[1,0,0,1,1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0],[1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,0,0,1,0,0],[0,1,0,0,0,0,0,0,0,1,0,1,0,0,0,0,0,0,0,0,0,1,0,0],[0,1,0,0,0,1,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0],[0,0,0,0,1,0,0,0,1,1,0,0,0,0,1,0,0,0,0,0,0,0,0,0],[1,0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0],[0,0,0,0,0,0,1,0,0,0,0,0,0,1,1,0,0,0,1,0,0,0,0,0],[0,0,0,0,0,1,0,0,0,0,1,0,1,0,0,1,0,0,0,0,0,0,0,0],[0,1,0,1,0,1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,1,1,0,1,0,0,0,0,0,0,0,0,0,0,0,1],[0,0,0,1,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,1,1],[0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,1,1,0,0,0,0,0,0,1],[0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,1,1,0,0,1,0,0,0,0],[0,0,0,0,1,1,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,1,0,0,0,1,1,1,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,1,1,0,0,0,0,0,1,1,0,0,0],[0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,0,1,0],[0,0,1,0,0,0,1,1,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,1,1,1,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,0,0,0,0,1,1],[1,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0],[0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,1,0,0,1,1,0,0],[0,0,0,0,0,0,0,0,0,0,1,1,1,0,0,0,0,0,0,0,1,0,0,0]];;
gamma := Graph( Group(()), [1..24], OnPoints, function(x,y) return A[x][y]=1;; end, true );;ag := AutGroupGraph( gamma );
ag := AutGroupGraph( gamma );
Display(StructureDescription(ag));
sg :=StrongGeneratorsStabChain(StabChain(ag));
oh := Group(sg);;
Display(oh);
P := PresentationViaCosetTable(oh);; TzPrint(P);
aa := ConjugacyClasses(oh);;
els := [];;
for a in aa do
for x in a do
Add(els, x);
od; od;
for i in [1..Length(sg)] do Print(Position(els, sg[i]), " "); od;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell10',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell10').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

## Finally

The following GAP code was used to save information about the groups to a local directory.

```{verbatim}
ElsByConjClass:=function(G)
  local els,cc,c,x,gens;
  gens := GeneratorsOfGroup(G);
  cc := ConjugacyClasses(G);
  els := [];
  for c in cc do
    for x in c do
      Add(els, x);
    od;
  od;
  return rec(names := ClassNames(CharacterTable(G)), sizes := List(cc, Size), 
  gens :=  List(gens, x -> Position(els, x)), elements := els);
end;;

SaveGroup := function(G, path, pts) 
  local els, e;
  els := ElsByConjClass(G);
  LogTo(path);
  Print("# ", StructureDescription(G), "\n# ", els.gens, "\n");
  P := PresentationViaCosetTable(G);; TzPrint(P);
  Print("# ", els.names, "\n# ", els.sizes, "\n");
  for e in els.elements do
  Print(ListPerm(e, pts),"\n");
  od;
  LogTo();
  return [];
end;;

pr:=Group( [ (3,5), (2,3)(4,5), (1,2)(4,6) ] );;
nsg:=NormalSubgroups(pr);;
path := Filename(DirectoryCurrent(), "r-projects/spantreeorbits/inst/extdata/");

SaveGroup(nsg[1], Concatenation(path, "oct_nsg1.txt"), 6);
SaveGroup(nsg[2], Concatenation(path, "oct_nsg2.txt"), 6);
SaveGroup(nsg[3], Concatenation(path, "oct_nsg3.txt"), 6);
SaveGroup(nsg[4], Concatenation(path, "oct_nsg4.txt"), 6);
SaveGroup(nsg[6], Concatenation(path, "oct_nsg6.txt"), 6);

ps := Group( [ (3,7)(4,6), (2,4)(5,7), (1,2)(3,4)(5,8)(6,7) ] );
SaveGroup(ps, Concatenation(path, "dic_lf.txt"), 8);

pt := Group( [ (3,5), (2,3)(4,5), (1,2)(4,6) ] );
SaveGroup(pt, Concatenation(path, "dic_rt.txt"), 6);

pu := Group( [ ( 2, 3)( 5, 7)( 8,12)( 9,11), ( 2, 9)( 3,11)( 4,10)( 5, 8)( 7,12), 
  ( 1, 2)( 3, 4)( 5, 9)( 6, 8)(10,12) ] );
SaveGroup(pu, Concatenation(path, "co.txt"), 12);

pv := Group( [ ( 2, 3)( 4, 5)( 8, 9)(12,13), ( 1, 2)( 4, 6)( 8,10)(11,12), 
  ( 1, 5, 4)( 2, 6, 3)( 7, 8, 9)(12,13,14), 
  ( 1, 6)( 2, 3)( 4, 5)( 7,11)( 8,12)( 9,13)(10,14) ] );
SaveGroup(pv, Concatenation(path, "dtc_lf.txt"), 14);

pw := Group( [ ( 2, 3)( 5, 7)( 8,12)( 9,11), ( 2, 9)( 3,11)( 4,10)( 5, 8)( 7,12), 
  ( 1, 2)( 3, 4)( 5, 9)( 6, 8)(10,12) ] );
SaveGroup(pw, Concatenation(path, "dtc_rt.txt"), 12);

px := Group( [ ( 2, 7)( 3,22)( 4,19)( 6,15)( 8,10)( 9,16)(11,14)(12,20)(17,24)
    (18,23), ( 1, 2, 5, 7)( 3, 4, 6, 8)( 9,14,18,12)(10,15,19,22)(11,16,20,23)
    (13,17,21,24), ( 1, 3,22)( 2,19,23)( 4, 7,18)( 5,20,12)( 6,14,24)
    ( 8,21,10)( 9,16,13)(11,15,17) ] );
SaveGroup(px, Concatenation(path, "rco.txt"), 24);

```

Then the following R code was used to create R objects from the save GAP output.

```{r eval=FALSE}
convert_gap_to_r <- function(infile, pts) {
  gaptext <- readLines(infile) 
  desc <- gaptext[1] %>% str_sub(3);
  gens <- eval(parse(text = str_c(gaptext[2],collapse = '') %>% 
                       str_replace("# \\[", "c(") %>% 
                       str_replace("\\]", ")")))
  cn <-  eval(parse(text = str_c(gaptext[3],collapse = '') %>% 
                      str_replace("# \\[", "c(") %>% 
                      str_replace("\\]", ")")))
  ci <-  eval(parse(text = gaptext[4] %>% str_replace("# \\[", "c(") %>% 
                      str_replace("\\]", ")")))
  names <- c()
  for(j in 1:length(ci)) {
    names <- c(names, str_c(cn[j],'.',1:ci[j]))
  }
  
  mx <- gaptext[5:length(gaptext)] %>% 
    str_replace_all('(\\[|\\])', '') %>%
    str_replace_all(' ', '') %>% 
    str_c(collapse = ',') %>% str_split_1(',') %>% 
    as.integer() %>% matrix(byrow = T, ncol = pts)
  
 list(description = desc,
      generators = gens,
      ids = names,
      elements = mx
  )
}
```

The r objects were copied into the data folder of this package.

```{r eval=FALSE}
fnames <- rbind(
  c("oct_nsg1.txt","c2xs4_aut_oct"),
  c("oct_nsg2.txt","c2xa4_oct"),
  c("oct_nsg3.txt","s4lf_oct"),
  c("oct_nsg4.txt","s4rt_oct"),
  c("oct_nsg6.txt","as4_oct"),
  c("dic_lf.txt","c2xs4_cu"),
  c("dic_rt.txt","c2xs4_oct"),
  c("co.txt","c2xs4_co"),
  c("dtc_lf.txt","c2xs4_rad"),
  c("dtc_rt.txt","c2xs4_aut_co"),
  c("rco.txt","c2xs4_rco")
)
pts <- c(6,6,6,6,6,8,6,12,14,12,24)

indir <- "./subtrees/"
outdir <- "../spantreeorbits/data/"

for(i in 1:nrow(fnames)) {
  obj <- convert_gap_to_r(str_c(indir, fnames[i,1]), pts[i])
  assign(fnames[i,2], obj)
  save(list = fnames[i,2], file = str_c(outdir, fnames[i,2], ".rda"))
}

```
