---
title: "Pair_Alignment"
author: "Jeff Lansing"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pair_Alignment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
.caption {
  margin: auto;
  text-align: center;
}

```{r setup, echo = FALSE, warning=FALSE}
library(stringr)
library(spantreeorbits)
source("./rgl_setup.R")
rgl::setupKnitr(autoprint = TRUE)
```

```{=html}
<script type="text/javascript" id="MathJax-script" async
  src="https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js">
</script>
```

## Introduction

The goal of this vignette is to use the common expansion of a polyhedron $\pi$ and its dual $\delta$ as a way to align $\pi$ with $\delta$. (For now we assume without proof that the two expansions are equal. We can see an illustration of this idea for the expansion of the tetrahedron [eT](https://levskaya.github.io/polyhedronisme/?recipe=eT) and for the expansion of the dual of the tetrahedron [edT](https://levskaya.github.io/polyhedronisme/?recipe=edT), at these links).

## Aligning the tetrahedron and its dual

```{r get_polys, echo=FALSE}
data(tetrahedron, package = "spantreeorbits")
data(octahedron, package = "spantreeorbits")
data(dual_tetrahedron, package = "spantreeorbits")
data(rhombic_dodecahedron, package = "spantreeorbits")
data(deltoidal_icositetrahedron, package = "spantreeorbits")
data(rhombicuboctahedron, package = "spantreeorbits")
data(deltoidal_tetracontaoctahedron, package = "spantreeorbits")
```
```{r}
rad <- rhombic_dodecahedron
tet <- tetrahedron
dtet <- dual_tetrahedron
oct <- octahedron
rad$texts <- rep("", 14)
```
:::: {style="display: flex; align-content: flex-start;"}
::: {}

```{r fig.cap=c("Figure 1a. A rhombic dodecahedron \\\n containing an octahedron")}
display_poly(rad, dual = oct, 
             scale = 0.8660254, zoom = 0.65)
```
:::
::: {}

```{r fig.cap=c("Figure 1b. A rhombic dodecahedron \\\n containing tetrahedra")}
display_poly(rad, dual = tet, codual = dtet, 
             scale = 1, zoom = 0.65)
```
:::
::::
<br>
The octahedron **_aligns_** the two tetrahedra in the following sense. Call the vertices where the rhombic dodecahedron intersects the octahedron _f-vertices_, and where it intersects the tetrahedra _t-vertices_ and _s-vertices_, respectively. Observe in Figures 1a and 1b above that each _f-vertex_ has 2 _t-vertices_ and 2 _s-vertices_ as neighbors. Then that _f-vertex_ _aligns_ the edge of the tetrahedron between the 2 _t-vertices_ with the edge of the dual tetrahedron between the 2 _s-vertices_.

We easily get the following alignment table mapping the edges of the tetrahedron to the edges of its dual:
\[
\begin{array}{|oct|tet|dual|}
  \hline
  f_1 & t_1t_3 & s_2s_4 \\
  \hline
  f_2 & t_2t_4 & s_1s_3 \\
  \hline 
  f_3 & t_1t_2 & s_1s_2 \\
  \hline
  f_4 & t_3t_4 & s_3s_4 \\
  \hline 
  f_5 & t_2t_3 & s_2s_3 \\
  \hline
  f_6 & t_1t_4 & s_1s_4 \\
  \hline 
\end{array}
\]

<!-- We can also produce this table autonatically. If we apply the vertex labels to the outer polygon in the order shown, and make a graph of the skeleton of that polygon, then we can manipulate the names of the neighbors of the _f-vertices_, as follows. -->
<!-- ```{r} -->
<!-- rad$texts <- c(str_c('f',1:6), str_c('s',1:4), str_c('t',1:4))[c(1:6,8,12,11,7,13,9,10,14)] -->
<!-- rad$texts -->

<!-- edges <- rad$texts[rad$segments %>% rownames() %>% as.integer()] %>%  -->
<!--   matrix(byrow = T, ncol = 2) -->

<!-- g <- edges %>% igraph::graph_from_edgelist(directed = F)  -->

<!-- igraph::E(g) -->

<!-- nghmap <- lapply(1:6, function(k) { -->
<!--   txt <- rad$texts[k] -->
<!--   ngh <- igraph::neighbors(g, txt) -->
<!--   vals <- names(ngh) %>% sort() %>% str_remove_all("(s|t)") %>% as.numeric() -->
<!--   c(sort(vals[1:2]), sort(vals[3:4])) -->
<!-- }) %>% abind::abind(along = 2) %>% t() %>% `[`(TRUE,c(3,4,1,2)) -->

<!-- nghmap -->

<!-- ``` -->

<!-- Actually, the work that was just illustrated here was already done when the rhombic dodecahedron was constructed. -->

<!-- ```{r} -->
<!-- identical(nghmap, rhombic_dodecahedron$nghmap) -->
<!-- ``` -->


## Aligning the cube and the octahedron

```{r}
dic <- deltoidal_icositetrahedron
cu <- cube
oct <- octahedron
co <- cuboctahedron
co$texts <- str_c('o', 1:12)
dic$texts <- rep("", 26)
```
<div>
:::: {style="display: flex; align-content: flex-start;"}
::: {}

```{r fig.cap=c("Figure 2a. A deltoidal icositetrahedron \\\n containing a cuboctahedron")}
display_poly(dic, dual = co, 
             scale = 0.9185587, zoom = 0.65)
```
:::
::: {}

```{r fig.cap=c("Figure 2b. A deltoidal icositetrahedron \\\n containing a cube and an octahedron")}
display_poly(dic, dual = cu, codual = oct, 
              coscale = 0.8660254, zoom = 0.65)
```
:::
::::
</div>
<br>

## Aligning the rhombic dodecahedron and the cuboctahedron

```{r}
dtco <- deltoidal_tetracontaoctahedron
dtco$texts <- rep("", 50)
rco <- rhombicuboctahedron
```
<div>
:::: {style="display: flex; align-content: flex-start;"}
::: {}

```{r fig.cap=c("Figure 3a. A deltoidal tetracontaoctahedron \\\n containing a deltoidal_icositetrahedron")}
display_poly(dtco, dual = rco, 
             scale = 0.9280776, zoom = 0.65)
```
:::
::: {}

```{r fig.cap=c("Figure 3b. A deltoidal tetracontaoctahedron containing \\\n a rhombic dodecahedron and a cuboctahedron")}
display_poly(dtco, dual = co, codual = rhombic_dodecahedron, 
             scale = 0.9185587, coscale = 1, zoom = 0.65)
```
:::
::::
</div>
<br>


```{r}
dtco$info
```


