---
title: "Pair_Alignment"
author: "Jeff Lansing"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pair_Alignment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css}
.caption {
  margin: auto;
  text-align: center;
}

```{r setup, echo = FALSE, warning=FALSE}
library(stringr)
library(spantreeorbits)
source("./rgl_setup.R")
rgl::setupKnitr(autoprint = TRUE)
```

## Introduction

The goal of this vignette is to use the common expansion of a polyhedron $\pi$ and its dual $\delta$ as a way to align $\pi$ with $\delta$. (For now we assume without proof that the two expansions are equal. But we can see an illustration for [eT](https://levskaya.github.io/polyhedronisme/?recipe=eT) and for [edT](https://levskaya.github.io/polyhedronisme/?recipe=edT), which is the case for the tetrahedron and its dual).

```{r get_polys, echo=FALSE}
data(tetrahedron, package = "spantreeorbits")
data(dual_tetrahedron, package = "spantreeorbits")
data(rhombic_dodecahedron, package = "spantreeorbits")
```

```{r display1, fig.align='center', fig.cap=c("Figure 1. A rhombic dodecahedron containing tetrahedra"), fig.height=4, fig.width=6}
rad <- rhombic_dodecahedron
tet <- tetrahedron
dtet <- dual_tetrahedron
rad$texts <- NULL
display_poly(rad, dual = tet, codual = dtet, scale = 1.5, theta = 103, phi = 7, zoom = 0.65)
```

