---
title: "Pair_Alignment"
author: "Jeff Lansing"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pair_Alignment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
.caption {
  margin: auto;
  text-align: center;
}
```

```{r setup, echo = FALSE, warning=FALSE}
library(stringr)
library(spantreeorbits)
source("./rgl_setup.R")
rgl::setupKnitr(autoprint = TRUE)
```

```{=html}
<script type="text/javascript" id="MathJax-script" async
  src="https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js">
</script>
```

## Introduction

The goal of this vignette is to use the common expansion of a polyhedron $\pi$ and its dual $\delta$ as a way to align $\pi$ with $\delta$. (For now we assume without proof that the two expansions are equal. We can see an illustration of this idea for the expansion of the tetrahedron [eT](https://levskaya.github.io/polyhedronisme/?recipe=eT) and for the expansion of the dual of the tetrahedron [edT](https://levskaya.github.io/polyhedronisme/?recipe=edT), at these links).

## Aligning the tetrahedron and its dual

```{r get_polys, echo=FALSE}
data(tetrahedron, package = "spantreeorbits")
data(cube, package = "spantreeorbits")
data(octahedron, package = "spantreeorbits")
data(dual_tetrahedron, package = "spantreeorbits")
data(rhombic_dodecahedron, package = "spantreeorbits")
data(deltoidal_icositetrahedron, package = "spantreeorbits")
data(rhombicuboctahedron, package = "spantreeorbits")
data(deltoidal_tetracontaoctahedron, package = "spantreeorbits")
```

```{r fig.align = 'center', fig.cap=c("Figure 1a. A cube containing a tetrahedron (red) \\\n and a dual tetrahedron (green).")}
display_poly(cube, dual = tetrahedron, codual = dual_tetrahedron, jitter = T, zoom = 0.95)


rbind(cube$texts, c(tetrahedron$texts, dual_tetrahedron$texts)) %>% 
  apply(1, function(rw) {str_c(rw, collapse = ',')}) %>% matrix(ncol = 1)

```

```{r fig.align = 'center', fig.cap=c("Figure 1b. A rhombic_dodecahedron containing a cube (red) \\\n and an octahedron (green).")}
display_poly(rhombic_dodecahedron, dual = cube, 
             codual = octahedron, coscale = 0.8660254, jitter = T)

rbind(rhombic_dodecahedron$texts, 
      c(octahedron$texts, cube$texts),
      c(rep("__",6), tetrahedron$texts, dual_tetrahedron$texts)) %>% 
  apply(1, function(rw) {str_c(rw, collapse = ',')}) %>% matrix(ncol = 1)

```
```{r fig.align = 'center', fig.cap=c("Figure 1c. A rhombic_dodecahedron containing a tetrahedron (red) \\\n and a dual tetrahedron (green).")}
display_poly(rhombic_dodecahedron, dual = tetrahedron, codual = dual_tetrahedron, jitter = T)

```
<br>
The octahedron **_aligns_** the two tetrahedra in the following sense. Call the vertices where the rhombic dodecahedron intersects the octahedron _f-vertices_, and where it intersects the tetrahedra _t-vertices_ and _s-vertices_, respectively. Observe in Figure 1c above that each _f-vertex_ has 2 _t-vertices_ and 2 _s-vertices_ as neighbors. Then that _f-vertex_ _aligns_ the edge of the tetrahedron between the 2 _t-vertices_ with the edge of the dual tetrahedron between the 2 _s-vertices_.

We easily get the following alignment table showing the mapping the edges of the tetrahedron to the edges of its dual The rows of the table correspond to the _f-vertices_, in order.
\[
\begin{array}{|oct|tet|dual|}
  \hline
  f_1 & t_1t_4 & s_2s_3 \\
  \hline
  f_2 & t_1t_2 & s_1s_3 \\
  \hline 
  f_3 & t_1t_3 & s_1s_2 \\
  \hline
  f_4 & t_3t_4 & s_2s_4 \\
  \hline 
  f_5 & t_2t_4 & s_3s_4 \\
  \hline
  f_6 & t_2t_3 & s_1s_4 \\
  \hline 
\end{array}
\]


Actually, the mapping that was just illustrated was already done when the rhombic dodecahedron was constructed.

```{r}
rhombic_dodecahedron$nghmap
```


## Aligning the cube and the octahedron

```{r fig.align = 'center', fig.cap=c("Figure 2a. A rhombic_dodecahedron containing a cube (red) \\\n and an octahedron (green).")}
display_poly(rhombic_dodecahedron, dual = cube, 
             codual = octahedron, coscale = 0.8660254, jitter = T)
```

```{r fig.align = 'center', fig.cap=c("Figure 2b. A deltoidal icositetrahedron containing a rhombic_dodecahedron (red) \\\n and a cuboctahedron (green).")}
display_poly(deltoidal_icositetrahedron, dual = rhombic_dodecahedron, scale = 1.01, 
             codual = cuboctahedron, coscale = 0.9185587, jitter = T)

rbind(deltoidal_icositetrahedron$texts, 
      c(rhombic_dodecahedron$texts[1:6], cuboctahedron$texts, rhombic_dodecahedron$texts[7:14]),
      c(octahedron$texts, rep("__",9), rep("___",3), cube$texts),
      c(rep("__",15), rep("___",3), tetrahedron$texts, dual_tetrahedron$texts)
      ) %>% 
  apply(1, function(rw) {str_c(rw, collapse = ',')}) %>% matrix(ncol = 1)

```
```{r fig.align = 'center', fig.cap=c("Figure 2c. A deltoidal icositetrahedron containing a cub (red) \\\n and an octahedron (green).")}
display_poly(deltoidal_icositetrahedron, dual = cube, 
             codual = octahedron, coscale = 0.8660254, jitter = T)

deltoidal_icositetrahedron$nghmap


```

<br>

## Aligning the rhombic dodecahedron and the cuboctahedron

```{r fig.align = 'center', fig.cap=c("Figure 3a. A deltoidal icositetrahedron containing a rhombic_dodecahedron (red) \\\n and a cuboctahedron (green).")}
display_poly(deltoidal_icositetrahedron, dual = rhombic_dodecahedron, scale = 1.01, 
             codual = cuboctahedron, coscale = 0.9185587, jitter = T)
```

```{r fig.align = 'center', fig.cap=c("Figure 3b. A deltoidal tetracontaoctahedron containing a deltoidal_icositetrahedron (red) \\\n and a rhombicuboctahedron (green).")}
display_poly(deltoidal_tetracontaoctahedron, dual = deltoidal_icositetrahedron, scale = 1, 
             codual = rhombicuboctahedron, coscale = 0.9280776, jitter = T)
```

```{r fig.align = 'center', fig.cap=c("Figure 3c. A deltoidal tetracontaoctahedron containing a rhombic_dodecahedron (red) \\\n and a cuboctahedron (green).")}
display_poly(deltoidal_tetracontaoctahedron, dual = rhombic_dodecahedron, scale = 1, 
             codual = cuboctahedron, coscale = 0.9185587, jitter = T)

deltoidal_tetracontaoctahedron$nghmap

rbind(deltoidal_tetracontaoctahedron$texts, 
      c(cuboctahedron$texts, rep("__",9), rep("___",15), rhombic_dodecahedron$texts)
) %>% 
  apply(1, function(rw) {str_c(rw, collapse = ',')}) %>% matrix(ncol = 1)

```


