---
title: "Source_Data_Sets"
author: "Jeff Lansing"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Source_Data_Sets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
require(magrittr)
require(stringr)
require(knitr)
require(kableExtra)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
.caption {
  margin: auto;
  text-align: center;
}
```
```{r setup, echo = FALSE, warning=FALSE}
library(stringr)
library(magrittr)
library(spantreeorbits)
source("./rgl_setup.R")
rgl::setupKnitr(autoprint = TRUE)
```

```{=html}
<script type="text/javascript" id="MathJax-script" async
  src="https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js">
</script>
```

## Introduction

The goal of this vignette is to describe the process for getting the source data sets. These sets constitute the "raw material" from which the spanning trees are "extracted", as explained below.

* The following assumptions will be in effect:
  + spanning trees come in pairs,
  + the pairs correspond to pairs of polyhedra,
  + the disjoint union of the edges of a spanning tree pair forms the edges of a spanning tree of the polyhedron that aligns the corresponding polyhedron pair,
  + the source data ultimately derives from a symmetric group with order equal to the vertex count of the aligning polyhedron.
  
In this vignette we look at 3 cases.

* For each case, the process is the following:
  + get the symmetric group of the appropriate order,
  + find a subgroup that is the direct product of symmetric groups that correspond to the appropriate pair of polyhedra,
  + compute the cosets of the subgroup in the initial symmetric group.
  
The computed cosets will be the source data for this case.
  
## Source Data for the Tetrahedron and the Dual Tetrahedron Spanning Trees

There are 2 candidates for the source data for the spanning trees of the tetrahedron and the dual tetrahedron.

As shown in the [Pair_Alignment](Pair_Alignment.html) vignette, the symmetric group $S_6$ is appropriate for this case, and the subgroup will be $S_3 \times S_3$. There will be $|S_{6}|/|S_3 \times S_3| = 20$ cosets. Actually we find 2 such subgroups; we list the corresponding cosets side by side.

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell2">
<script type="text/x-sage">
s6 := SymmetricGroup(6);;
ll6 := LowLayerSubgroups(s6,1);;
Display(List(ll6, Order));
wh := Position(List(ll6, Order), 72);;
s3s3c2 := ll6[wh];;
ll66 := LowLayerSubgroups(s3s3c2,1);;
whs := Positions(List(ll66, Order), 36);;
rt2:=RightTransversal(s6, ll66[whs[1]]);;
lr2 := List(rt2, x -> ListPerm(x,6));;
rt3:=RightTransversal(s6, ll66[whs[2]]);;
lr3 := List(rt3, x -> ListPerm(x,6));;
for i in [1..Length(rt2)] do Print(lr2[i], "\t", lr3[i], "\n");; od;;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell2',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell2').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

The group $S_6$ has $S_3^2 \rtimes C_2$ as an immediate subgroup. In turn, $S_3^2 \rtimes C_2$ has 2 copies of $S_3 \times S_3$ as immediate subgroups. The cosets of these 2 copies in $S_6$ are shown by evaluating the above GAP code, and also below. (The whole subgroup lattice of $S_3^2 \rtimes C_2$ is shown at [GroupNames](https://people.maths.bris.ac.uk/~matyd/GroupNames/61/S3wrC2.html).)

Note that these two tables illustrate the third assumption; a center dividing line helps to show this.

```{r results ='asis', echo=FALSE}
path <- system.file("extdata", "s3s3c2.txt", package = "spantreeorbits", mustWork = TRUE)
gaptext <- readLines(con = path) 
t <- gaptext %>% 
  str_replace_all(' \\.\\. ', ', 2, 3, 4, 5,') %>% 
  str_replace_all('\\]\\s+\\[', ', ') %>% 
  str_replace_all('(\\[|\\])', '') %>% 
  str_c(collapse = ',') %>% str_c('c(', ., ')')
vals <- eval(parse(text = t)) %>% `dim<-`(c(6,2,20)) %>% aperm(c(3,1,2))

knitr::kable(
  vals[,,1],
  caption = "cosets of $S_3 \\times S_3$ left",
  format = "html",
  escape = FALSE,
  align = 'c',
  col.names = NULL) %>% kableExtra::kable_styling(
  full_width = F, position = "float_left") %>% 
  kableExtra::column_spec(c(1:6), width = "1.1em") %>% 
  kableExtra::column_spec(c(3,6), border_right = T) %>% 
  kableExtra::column_spec(c(1), border_left = T)

knitr::kable(
  vals[,,2],
  caption = "cosets of $S_3 \\times S_3$ right",
  format = "html",
  escape = FALSE,
  align = 'c',
  col.names = NULL) %>% kableExtra::kable_styling(
  full_width = F, position = "left") %>% 
  kableExtra::column_spec(c(1:6), width = "1.1em") %>% 
  kableExtra::column_spec(c(3,6), border_right = T) %>% 
  kableExtra::column_spec(c(1), border_left = T)

```


## Source Data for the Cube and the Octahedron Spanning Trees

As shown in the [Pair_Alignment](Pair_Alignment.html) vignette, the symmetric group $S_{12}$ is appropriate for this case, and the corresponding subgroup will be $S_7 \times S_5$. There will be $|S_{12}|/|S_7 \times S_5| = 792$ cosets.

```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell3">
<script type="text/x-sage">
s12 := SymmetricGroup(12);;
ord75 := Order(DirectProduct(SymmetricGroup(7),SymmetricGroup(5)));
ll12 := LowLayerSubgroups(s12,1);;
wh75 := Position(List(ll12, Order), ord75);;
s7s5 := ll12[wh75];;
Display(StructureDescription(s7s5));
rt75:=RightTransversal(s12, s7s5);;
Display(Length(rt75));
lr75 := List(rt75, x -> ListPerm(x,12));;
for i in [1..20] do Print(Random(lr75),"\n");; od;;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell3',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell3').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

The group $S_{12}$ has (what GAP calls) $S_5 \times S_7$ as an immediate subgroup. A random sample of the cosets of this subgroup in $S_{12}$ is shown by evaluating the above GAP code, and also below. (It seems by inspection of the cosets that it would be appropriate to call the subgroup $S_7 \times S_5$.)

```{r results ='asis', echo=FALSE}
path <- system.file("extdata", "s5s7sample20.txt", package = "spantreeorbits", mustWork = TRUE)
gaptext <- readLines(con = path) 
t <- gaptext %>% 
  str_replace_all('(\\[|\\])', '') %>% 
  str_c(collapse = ',') %>% str_c('c(', ., ')')
vals <- eval(parse(text = t)) %>% matrix(byrow = T, ncol = 12)

knitr::kable(
  vals,
  caption = "cosets of $S_7 \\times S_5$",
  format = "html",
  escape = FALSE,
  align = 'c',
  col.names = NULL) %>% kableExtra::kable_styling(
  full_width = F, position = "center") %>% 
  kableExtra::column_spec(c(1:12), width = "1.1em") %>% 
  kableExtra::column_spec(c(7,12), border_right = T) %>% 
  kableExtra::column_spec(c(1), border_left = T)
```

## Source Data for Rhonbic Dodecahedron and the Cuboctahedron Spanning Trees

As shown in the [Pair_Alignment](Pair_Alignment.html) vignette, the symmetric group $S_{24}$ is appropriate for this case, and the corresponding subgroup will be $S_{13} \times S_{11}$. There will be $|S_{24}|/|S_{13} \times S_{11}| = 2496144$ cosets.


```{=html}
<div>
<script src="https://sagecell.sagemath.org/static/embedded_sagecell.js" data-external="1"></script>
<div id="cell4">
<script type="text/x-sage">
s24 := SymmetricGroup(24);;
ll24 := LowLayerSubgroups(s24,1);;
o1311 := Order(DirectProduct(SymmetricGroup(13), SymmetricGroup(11)));
wh := Position( List(ll24, Order), o1311);
Display(StructureDescription(ll24[wh]));
Warning("The following code will timeout.");
rt:=RightTransversal(s24, ll24[wh]);;
lrc := List(rt, x -> ListPerm(x,24));;
for i in [1..20] do Print(Random(lrc),"\n");; od;;
</script>
</div>
<script>
sagecell.makeSagecell({
inputLocation: '#cell4',
languages: ['gap'],
//Focus the editor
callback: function() {$('#cell4').find(".CodeMirror").get(0).CodeMirror.focus();}
});
</script>
</div>
```

The group $S_{24}$ has (what GAP calls) $S_{11} \times S_{13}$ as an immediate subgroup. A random sample of the cosets of this subgroup in $S_{24}$ is shown  below. (It seems by inspection of the cosets that it would be appropriate to call the subgroup $S_{13} \times S_{11}$.)

```{r results ='asis', echo=FALSE}
path <- system.file("extdata", "s11s13sample20.txt", package = "spantreeorbits", mustWork = TRUE)
gaptext <- readLines(con = path) 
t <- gaptext %>% 
  str_replace_all('(\\[|\\])', '') %>% 
  str_c(collapse = ',') %>% str_c('c(', ., ')')
vals <- eval(parse(text = t)) %>% matrix(byrow = T, ncol = 24)

knitr::kable(
  vals,
  caption = "cosets of $S_{13} \\times S_{11}$",
  format = "html",
  escape = FALSE,
  align = 'c',
  col.names = NULL) %>% kableExtra::kable_styling(
  full_width = F, position = "center") %>% 
  kableExtra::column_spec(c(1:24), width = "1.1em") %>% 
  kableExtra::column_spec(c(13,24), border_right = T) %>% 
  kableExtra::column_spec(c(1), border_left = T)
```

## Finally

The three source sets were generated locally using the GAP code shown, and then saved to disk locally by GAP, as rows in GAP List format. Using a text editor capable of handling files with millions of lines, the brackets were removed to produce a file in csv format. This file was then converted to rda format outside of this package, using the code shown below,and then copied into the source for this package.

```{r eval=FALSE}

path <- system.file("extdata", "s3s3c2.txt", package = "spantreeorbits", mustWork = TRUE)
gaptext <- readLines(con = path) 
t <- gaptext %>% 
  str_replace_all(' \\.\\. ', ', 2, 3, 4, 5,') %>% 
  str_replace_all('\\]\\s+\\[', ', ') %>% 
  str_replace_all('(\\[|\\])', '') %>% 
  str_c(collapse = ',') %>% str_c('c(', ., ')')
oct_source_data <- eval(parse(text = t)) %>%
  as.integer() %>% `dim<-`(c(6,2,20)) %>% aperm(c(3,1,2))
save(oct_source_data, file = "./extdata/oct_source_data.rda")

vals <- read.csv(file = "./subtrees/s7s5reps.csv", header = F)
cuboct_source_data <- vals %>% data.matrix() %>% `colnames<-`(NULL)
save(cuboct_source_data, file = "./extdata/cuboct_source_data.rda")

vals <- read.csv(file = "./subtrees/s13s11reps.csv", header = F)
rhombicuboct_source_data <- vals %>% data.matrix() %>% `colnames<-`(NULL)
save(rhombicuboct_source_data, file = "./extdata/rhombicuboct_source_data.rda")

```
